A Modular Handwritten Kanji Recognition Schema

### 2014-09-05 doc/tacs2014/article.tex
Decided to remove last 'basic' after all

	\begin{abstract}
		Handwriting continues to play a significant role in daily life, warranting continued research in the field of intelligent character recognition.
		%Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
		East asian scripts, such as Japanese, remain challenging to process efficiently with high accuracy due to their vast number of symbols.
		In this work, a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs is presented, along with
		the description of an ongoing effort to implement and evaluate a basic handwriting recognition system that incorporates online feature extraction,
		category clustering, and artificial neural networks.

>>>>

	\begin{abstract}
		Handwriting continues to play a significant role in daily life, warranting continued research in the field of intelligent character recognition.
		%Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
		East asian scripts, such as Japanese, remain challenging to process efficiently with high accuracy due to their vast number of symbols.
		In this work, a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs is presented, along with
		the description of an ongoing effort to implement and evaluate a handwriting recognition system that incorporates online feature extraction,
		category clustering, and artificial neural networks.
